The Chemistry Development Kit (CDK): atom typing, rendering, molecular formulas, and substructure searching

### 2016-10-05 article.tex
BMC doesn't have that 'e'

%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Acknowledgements}
The authors acknowledge the great number of people who have contributed smaller
and larger contributions to the CDK library. A full list of contributors is
found in the AUTHORS file~\cite{AUTHORS}. OS acknowledges support from the Swedish strategic research programs eSSENCE and Swedish e-Science Research Center (SeRC). TP is a Simons Foundation Fellow of the Helen Hay Whitney Foundation.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Acknowledgments}
The authors acknowledge the great number of people who have contributed smaller
and larger contributions to the CDK library. A full list of contributors is
found in the AUTHORS file~\cite{AUTHORS}. OS acknowledges support from the Swedish strategic research programs eSSENCE and Swedish e-Science Research Center (SeRC). TP is a Simons Foundation Fellow of the Helen Hay Whitney Foundation.
